---
title: "README"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Installation

##Via github

1. make sure that devtools is installed

```{r installdevt,eval=FALSE}
install.packages('devtools')
```
####On Windows:
there is a known bug that R freezes when installing the package 'BH' automatically, as a dependency of ggplot. Therefore, install it manually by running the the following command first.
```{r bhwindows,eval=FALSE}
install.packages('BH')
```

then execute

```{r install,eval=FALSE}
require(devtools)
devtools::install_github('alxbetz/bendr')
```


##Troubleshooting
If you see an error about libssh2 missing, on UNIX based systems, you need to install libssh2 and on Windows, it is recommended to just update the 'git2r' package(update.packages('git2r'))

###Installing libssh2
###On linux
Use your favourite package manager(e.g. APT,yum) 

```{bash libssh2lin,eval=FALSE}
sudo apt-get install libssh2-1 libssh2-1-dev
sudo yum install libssh2
```

###On mac OS
First install Homebrew, a package manager for OS X
```{bash homebrew,eval=FALSE}
ruby -e "$(curl -fsSL https://raw.githubusercontent.com/Homebrew/install/master/install)" < /dev/null 2> /dev/null
```

then install libssh2 via homebrew

```{bash libssh2brew,eval=FALSE}
brew install libssh2
```

