---
title: "Dose response curve fitting examples"
author: "Alexander Betz"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{bendr-examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup,message=FALSE,warning=FALSE}
library(bendr)
library(tibble)
library(dplyr)
library(ggplot2)
```


You can read your data from csv,tsv or excel:
```{r datai,eval=FALSE}
fname = "/path/to/file"
require(readr)
fdata = readr::read_csv(fname)
fdata = readr::read_tsv(fname)
require(readxl)
fdata = readxl::read_excel(fname)
names(fdata)
View(fdata)
```


But for a quick test, we generate some dummy data:
```{r dummydata}
sdata = as_tibble(
  data.frame(
    conc=c(1,10,100,1000,5000),
    effect=c(12,27,69,86,98)
  ))

sdata = as_tibble(
  data.frame(
    conc=c(0.0001,0.001,0.01,0.1,1),
    effect=c(12,27,69,86,98)
  ))
```

then we set the formula for the dose response model

```{r formula100}
drc.formula = effect ~ 100 / (1 + 10^((logEC50-logconc) * slope))
```

if you want to adapt the dose response curve to the maximum and minimum effect values, use this formula instead

```{r formula.dyn}
loe = min(sdata$effect)
hie = max(sdata$effect)
drc.formula.dyn = substitute(
  effect ~ bottom + ((top-bottom)/(1+10^((logEC50-logconc)*slope))),
  list(top = hie, bottom=loe))
```



Here is an example for fitting a single dose-response curve
```{r singlefit}

data.logged = sdata %>% mutate(logconc = log10(conc))

fitObject = bendr::fitdr(drc.formula,data.logged)
summary(fitObject$curve.fit)
pSingle = plot_single_drc(fitObject) + xlab("log(concentration)") + ylab("effect")
pSingle 
#ggsave("/path/to/image.png",pSingle,width="8",height="6",units="in")
```

###Reporting goodness of fit
 R^2 is considered inadequate for nonlinear fits (https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2892436/)
 Instead, use akaike's An Information Criterion(AIC).

##Fitting multiple dose response curves simulatneously

```{r multifit}

mdata = as_tibble(
  data.frame(
    conc=c(1,10,100,1000,5000),
    effectA=c(12,27,69,86,98),
    effectB=c(15,23,64,82,91)
  ))

fo = fitdr_multi(drc.formula,mdata,2:3,conc)
pMulti = plot_multi_drc(fo,plot.layout='multi')
pMulti
```

##Fitting a single dose response curve to the mean of replicates


```{r replifit}
rdata = as_tibble(
  data.frame(
    conc=c(0.1,1,10,100,1000,5000),
    replicateA=c(1,12,27,65,88,100),
    replicateB=c(2,16,21,62,81,100),
    replicateC=c(4,15,21,61,85,96)
  ))

fitObjectRep = fitdr_replicates(drc.formula,rdata,2:4,conc)
pRep = plot_replicate_drc(fitObjectRep)
pRep
```
